Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by \textsc{DigitalSnow} ANR-11-BS02-009, \textsc{KIDICO} ANR-2010-BLAN-0205 and \textsc{PRIMES Labex} ANR-11-LABX-0063/ ANR-11-IDEX-0007 research grants.}

### 2015-10-22 latex/article.tex

As illustrated in Figure
\ref{fig_quadtree_partitionning}-\emph{middle}, we propose a viewpoint
dependent criterion to decide if a cell needs to be refined: the
closer we are to the camera, the finer the cells are. In addition to
the distance criterion, we define an angular criterion to prevent refining cells outside the camera frustrum. Using a criterion based on the distance between a cell and the camera is well suited to GPU since it can be evaluated independently on all cells. Hence, we can efficiently determine if a cell must be subdivided or not. Figure \ref{fig_lod_octree}
illustrates the level of details (LoD for short) criterion we
use. More precisely, in dimension 2, if $\alpha$ denotes the viewing
angle, an object at distance $d$ from the camera with diameter greater than
 $2\cdot d\cdot\tan(\alpha)$
 is projected into more than one pixel
(see Figure~\ref{fig_lod_octree}-\emph{left}). Hence, the distance
criterion is based on the ratio (\emph{visibility ratio} in the
following)between the cell diameter $l(c)$ (power of 2 depending on
the depth), and
$2\cdot d_c\cdot\tan(\alpha)$, $d_c$ being the distance between the cell center and the camera. For a given cell $c$,
split and merge decision are based on this visibility ratio:
\begin{itemize}
\item $c$ is split if its children cells have a visibility ratio
  greater than  constant $k$\,;
\item $c$ and its sibling cells are merged if their parent cell $c'$
  have av visibility ratio lower than $k$\;
\item otherwise, the cell $c$ stays for the next frame.
\end{itemize}
%
\begin{figure}[!h]
  \begin{center}
    \begin{overpic}[width=3.5cm]{figs/criterion}
      \put(33,40){$\alpha$}
      \put(50,45){$d_c$}
      \put(95,65){$l(c)$}
    \end{overpic}~~~~~
    \includegraphics[width=3.5cm]{viewlod2_small}~~~~~
    \includegraphics[width=3cm]{subdivision}
  \end{center}
  \caption{Notations \emph{(left)} and adaptive meshing in dimension 2 using the LoD distance and
    angular criterion \emph{(middle)}. Based on LoD criterion
    evaluation, the cell buffer is
  updated between each frame \emph{(right)}.}
  \label{fig_lod_octree}
\end{figure}
%
In addition to the distance criterion, we add an angular term in order
to prevent subdivision of cells far from the camera frustrum (see
Figure~\ref{fig_lod_octree}-\emph{middle}). We do not go into the
details but please note that stay, split and merge decisions of all cells are computed in
parallel from all cell morton codes.

Once decisions have been made, a new set of cells are sent to the mesh
generation step described above. Updating the cell buffer can be
efficiently implemented on GPU hardware as illustrated in
Figure~\ref{fig_lod_octree}-\emph{right}.  Finally, before
constructing the triangulation from remaining cells and transition
cells, geometrical culling is performed in order to skip the triangle
patch construction which are not visible. Figure \ref{fig_pipeline}
illustrates the overall fully data parallel pipeline.

>>>>

As illustrated in Figure~\ref{fig_quadtree_partitionning}-\emph{middle}, we
propose a viewpoint dependent criterion to decide if a cell needs to be refined:
the closer we are to the camera, the finer the cells are. In addition to the
distance criterion, we define an angular criterion to prevent refining cells
outside the camera frustrum. Using a criterion based on the distance between a
cell and the camera is well suited to GPU since it can be evaluated
independently on all cells. Hence, we can efficiently determine if a cell must
be subdivided or not. Figure~\ref{fig_lod_octree} illustrates the level of
details (LoD for short) criterion we use. More precisely, in dimension 2, if
$\alpha$ denotes the viewing angle, an object at distance $d$ from the camera
with diameter greater than $2\cdot d\cdot\tan(\alpha)$ is projected into more
than one pixel (see Figure~\ref{fig_lod_octree}-\emph{left}). Hence, the
distance criterion is based on the ratio (\emph{visibility ratio} in the
following) between the cell diameter $l(c)$ (power of 2 depending on the depth),
and $2\cdot d_c\cdot\tan(\alpha)$, $d_c$ being the distance between the cell
center and the camera. For a given cell $c$, split and merge decision are based
on this visibility ratio:
%
\begin{itemize}
  \item $c$ is split if its children
cells have a visibility ratio greater than  constant $k$\,;
  \item $c$ and its sibling cells are merged if their parent cell $c'$ has a visibility ratio lower than $k$\;
  \item otherwise, the cell $c$ stays for the next frame.
\end{itemize}
%
\begin{figure}[!h]
  \begin{center}
    \begin{overpic}[width=3.5cm]{figs/criterion}
      \put(33,40){$\alpha$}
      \put(50,45){$d_c$}
      \put(95,65){$l(c)$}
    \end{overpic}~~~~~
    \includegraphics[width=3.5cm]{viewlod2_small}~~~~~
    \includegraphics[width=3cm]{subdivision}
  \end{center}
  \caption{Notations \emph{(left)} and adaptive meshing in dimension 2 using the LoD distance and angular criterion \emph{(middle)}. Based on LoD criterion
    evaluation, the cell buffer is updated between each frame \emph{(right)}.}
  \label{fig_lod_octree}
\end{figure}
%
In addition to the distance criterion, we add an angular term in order
to prevent subdivision of cells far from the camera frustrum (see
Figure~\ref{fig_lod_octree}-\emph{middle}). We do not go into the
details but please note that stay, split and merge decisions of all cells are computed in
parallel from all cell morton codes.

Once decisions have been made, a new set of cells are sent to the mesh
generation step described above. Updating the cell buffer can be
efficiently implemented on GPU hardware as illustrated in
Figure~\ref{fig_lod_octree}-\emph{right}.  Finally, before
constructing the triangulation from remaining cells and transition
cells, geometrical culling is performed in order to skip the triangle
patch construction which are not visible. Figure~\ref{fig_pipeline}
illustrates the overall fully data parallel pipeline.
